# lmSubsets

[![](http://www.r-pkg.org/badges/version/lmSubsets)](https://cran.r-project.org/package=lmSubsets)
![](https://cranlogs.r-pkg.org/badges/grand-total/lmSubsets)


## Overview

Exact and approximation algorithms for variable-subset selection in
ordinary linear regression models.  Either compute all submodels with
the lowest residual sum of squares, or determine the single-best
submodel according to a pre-determined statistical criterion.
[Hofmann et al. (2020)](http://dx.doi.org/10.18637/jss.v093.i03).


## Installation

```{r, eval = FALSE}
# Install package from CRAN:
install.packages("lmSubsets")
```


## Usage

```{r, eval=TRUE}
# load package
library("lmSubsets")

# load some data
data("AirPollution", package = "lmSubsets")

head(AirPollution)
```

### All-subsets regression

```{r, eval=TRUE}
# compute 3 best submodels for every subset size
lm_all <- lmSubsets(mortality ~ ., data = AirPollution, nbest = 3)
lm_all
```

```{r, eval=TRUE}
# plot deviances and BICs
plot(lm_all)
```

```{r, eval=TRUE, fig.asp = (14 * 3 + 1) / (16 * 3)}
# plot heatmap, hilite 10 best submodels (BIC)
image(lm_all, best = 1:3, hilite = 1:10, hilite_penalty = "BIC")
```

```{r, eval=TRUE}
# evaluate summary statistics
summary(lm_all)
```

### Best-subset regression

```{r, eval=TRUE}
# compute 20 best (BIC) submodels
lm_best <- lmSelect(mortality ~ ., data = AirPollution, nbest = 20)
lm_best
```

```{r, eval=TRUE}
# plot deviances and BIC
plot(lm_best)
```

```{r, eval=TRUE}
# show heatmap
image(lm_best, hilite = 1)
```

```{r, eval=TRUE}
# evaluate summary statistics
summary(lm_best)
```


## Authors

```{r, eval=TRUE, echo=FALSE, results="hide"}
meta <- packageDescription("lmSubsets")
authors <- eval(parse(text = meta[["Authors@R"]]))
authors <- authors[sapply(authors, function (pers) "aut" %in% pers$role)]
maintainers_ix <- which(sapply(authors, function (pers) "cre" %in% pers$role))
authors <- format(authors, include = c("given", "family"))
authors[maintainers_ix] <- paste(authors[maintainers_ix], "(maintainer)")
authors <- paste(authors, collapse = ", ")
```
`r authors`
